Efficiently stable presentations from error-correcting codes

### 2023-09-27 efficient_stability.tex
typos in Section 3

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back} {\color{red} THERE IS NO O NOTATION HERE}), so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_a = w^* T_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* T_a w \big)^2 \big) \\
&= \sum_a \tau^\mM \big(  w^* T_a w w^*T_a w \big)\\
&= \sum_a \tau^\mM \big(  w^* T_a  P T_a w \big) - \sum_a \tau^\mM \big( w^* T_a  ( P - w w^*) T_a w \big)\\
&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* T_a  ( P - w w^*) T_a w \big)\\
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  T_a w w^* T_a\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the third line uses that $T_aPT_a=T_a$, $\sum_a T_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a T_a\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;,
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
\begin{equation*}
\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_\tau \,=\, 27\eps\;.
\end{equation*}
Finally,
\begin{align*}
\sum_a \big\|{Q}_a - w^*{T}_a w\big\|^2_\tau &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_\tau^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_\tau^2 \\
&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
&\leq 56 \eps\;,
\end{align*}
where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
\end{proof}

@@

\begin{proof}
Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation. Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$. Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$ {\color{red} THIS SHOULD BE $\mN$... THE REST OF THE PROOF REQUIRES MORE EXPLANATIONS}. Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.

For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$. Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$, and $U_x = \sum_u (-1)^{u\cdot x} Q_u$. Furthermore, it holds that 
\begin{equation}\label{eq:lin-test-1}
   \Es{x\in \Z_2^k} \Big\| \phi(x) - w^*\Big(\sum_u (-1)^{u\cdot x} Q_u\Big)w  \Big\|_{\tau}^2 \,=\, O(\eps)\;,
\end{equation}
for some partial isometry $w\in P\mM_\infty I_\mM$ as in Definition~\ref{def:close}.
Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mM$ that satisfies 
\[ \sum_u \big\| P_u - w^* Q_u w \big\|_\tau^2 \,=\, O(\eps)\;.\]
Combined with~\eqref{eq:lin-test-1} and the triangle inequality, this shows the corollary. 
\end{proof}

@@

As a first step, we introduce a general method for translating any binary linear error-correcting code into a presentation of $\Z_2^k$.

@@

For $q$ a prime power we let $\F_q$ denote the finite field with $q$ elements, and write $\F$ when $q=2$. 
For $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$. The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}. A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ such that $\code = \ker h$.

For the remainder of this section we specialize the discussion to the case where $q=2$. 
A parity check matrix for a code of dimension $k$ implies a presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e \]
that ``verifies'' the parity check associated with the $i$-th row of $h$. Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$ as 
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
\end{equation}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$, and not only on $\code$. If however we further impose all pairwise commutation relations then we obtain the following.

@@

\begin{proof}
The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$. In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$. So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.  
\end{proof}

\begin{remark}\label{rk:non-abelian}
There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see~\cite[Example 2.16]{paddock2022arkhipov}.  
\end{remark}

@@

\begin{definition}[$r$-local linear tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
%An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester. However, we will not need to be more specific than this. \hnote{This is probably a very vague comment that only makes sense to those who already know LTCs :)}} \hnote{Given that we've already talked about parity check matrices, it seems easier to define a local linear tester for a code $\code$ as a pair $(h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.}\tnote{Yes ok. I didn't change now but I'm in favor}
%\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. 
An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$. 
\end{definition}

@@

We state our first stability result for a code-based presentation, the presentation $G(h_\had)$ defined as~\eqref{eq:def-gh-pres} where $h_\had$ is defined above. To state the result we need to specify distributions $\mu_S$ and $\mu_R$. We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$. (Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$.)

\begin{lemma}\label{lem:had-stab}
Let $\mC$ be the class of all tracial von Neumann algebras. 
The presentation $\Z_2^t= G(h_\had)$, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=O(\eps)$. 
\end{lemma}

@@

Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$. Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
\[
	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
\]
where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$. It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$. It follows that the linear span of all $(f(x))_{x\in \F_q^m}$, when ranging over all possible $\{c_\alpha\}$, defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.

@@

We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$. The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}. %From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$. 
The description makes use of interpolation coefficients, which are defined as follows. %For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let 
%\begin{equation}\label{eq:interp-coeff}
% \alpha_{u,v,i} = \frac{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(v-(u+i')\big)}{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(u+i-(u+i')\big)}\;.
%\end{equation}
Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
 \begin{equation}\label{eq:interp-coeff}
 \alpha_{u,v,i} = \prod_{\substack{i'=0\\i'\neq i}}^{d}  \frac{v - (u + t_{i'})}{t_i - t_{i'}}~.
 \end{equation}
These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
%\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
that for all $v \in \F_q$, 
\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(v+t_i)\;.\]

@@

A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times q$ is as follows. Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times \F_q$. The $(u,j,t)$-th row of $h_{\RM}$ is the vector in $\F_q^m$ that for $i \in \{0,\ldots,d\}$ has the value $\alpha_{u,v,i}$ for $v = u + t e_j$ in the coordinate indexed by $u + t_i e_j$, the value $-1$ in the coordinate indexed by $u + te_j$, and the value $0$ everywhere else.

@@

Let $\kappa: \F_q \to \F_2^t$ denote an invertible linear map such that $\kappa(a)$ is the $\F_2$-representation of $a \in \F_q$ over some (implicitly specified) self-dual basis of $\F_q$ over $\F_2$. We extend $\kappa$ and its inverse $\kappa^{-1}$ to vectors over $\F_q$ coordinate-wise. We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$. Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$  where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$. For more details on the $\kappa$ map and its properties, see~\cite[Section 3.3]{ji2020mip}.

@@

Given an $r$-local $M=(h,\nu)$ for $\code$, there is a natural $r$-local tester $M'$ for $\code'$ which can be described as follows. Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.  We describe an $r$-local tester $M' = (h',\nu')$ for $\code'$. Informally, $h'$ contains two type of checks. First, the $A$-checks consist in the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$. Second, the $B$-checks implement the checks of $\code$ specified by $M$, directly on the Hadamard encoding. More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where 
\begin{itemize}
	\item $A \in \F^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
	\item $B \in \F^{\ell q \times nq}$ is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$. The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
\end{itemize}
Define the distribution $\nu'$ as the uniform mixture of the uniform distribution on the rows of the $A$ block matrix and the uniform distribution on the rows of the $B$ block matrix.

>>>>

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial, so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_a = w^* T_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* T_a w \big)^2 \big) \\
&= \sum_a \tau^\mM \big(  w^* T_a w w^*T_a w \big)\\
&= \sum_a \tau^\mM \big(  w^* T_a  P T_a w \big) - \sum_a \tau^\mM \big( w^* T_a  ( P - w w^*) T_a w \big)\\
&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* T_a  ( P - w w^*) T_a w \big)\\
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  T_a w w^* T_a\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the third line uses that $T_aPT_a=T_a$, $\sum_a T_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a T_a\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;,
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
\begin{equation*}
\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_\tau \,=\, 27\eps\;.
\end{equation*}
Finally,
\begin{align*}
\sum_a \big\|{Q}_a - w^*{T}_a w\big\|^2_\tau &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_\tau^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_\tau^2 \\
&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
&\leq 56 \eps\;,
\end{align*}
where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
\end{proof}

@@

\begin{proof}
Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation. Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$. Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mN$. Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.

For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$. Then each $Q_u$ is a projection on $\mN$ such that $\sum_u Q_u=\Id$, and $U_x = \sum_u (-1)^{u\cdot x} Q_u$. Furthermore, by the conclusion of Theorem~\ref{thm:gh} it holds that 
\begin{equation}\label{eq:lin-test-1}
   \Es{x\in \Z_2^k} \Big\| \phi(x) - w^*\Big(\sum_u (-1)^{u\cdot x} Q_u\Big)w  \Big\|_{\tau}^2 \,=\, O(\eps)\;,
\end{equation}
for some partial isometry $w\in P\mM_\infty I_\mM$ as in Definition~\ref{def:close}.
Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mM$ that satisfies 
\begin{equation}\label{eq:lin-test-1b}
 \sum_u \big\| P_u - w^* Q_u w \big\|_\tau^2 \,=\, O(\eps)\;.
\end{equation}
Thus
\begin{align}
\Es{x\in \Z_2^k}  \Big\| \sum_u (-1)^{u\cdot x} \big(P_u - w^* Q_u w\big) \Big\|_\tau^2
&=\Es{x\in \Z_2^k} \sum_{u,v} (-1)^{(u+v)\cdot x} \tau\big(\big(P_u - w^* Q_u w\big)\big(P_v - w^* Q_v w\big)\big) \notag\\
&= \sum_u \big\| P_u - w^* Q_u w\big\|_\tau^2\notag\\
&= O(\eps)\;,\label{eq:lin-test-2}
\end{align}
where the second line uses $\Es{x} (-1)^{w\cdot x} = 0$ if $w\neq 0$, and $1$ otherwise, and the last line is by~\eqref{eq:lin-test-1b}. Plugging back into~\eqref{eq:lin-test-1} and using the triangle inequality shows the corollary.  
\end{proof}

@@

As a first step, we introduce a general method for translating any binary linear error-correcting code into a presentation of $\Z_2^k$. Later we apply this method to the specific case of the Reed-Muller code (composed with the Hadamard code to obtain a binary code). However, the general method may be of independent interest.

@@

For $q$ a prime power we let $\F_q$ denote the finite field with $q$ elements. 
For $n,k,d$ integer, a $[n,k,d]_q$ linear code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$. The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}. A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ such that $\code = \ker h$.

For the remainder of this section we specialize the discussion to the case where $q=2$. 
We make the simple but key observation that a parity check matrix for a code of dimension $k$ implies a finite group presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e\;, \]
that ``verifies'' the parity check associated with the $i$-th row of $h$. Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$ as 
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
\end{equation}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$, and not only on $\code$. If however we further impose \emph{all} pairwise commutation relations then we obtain the following.

@@

\begin{proof}
The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$. In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq n} x_j^{h_{ij}}$. So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.  
\end{proof}

\begin{remark}\label{rk:non-abelian}
There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see~\cite[Example 2.16]{paddock2022arkhipov}. For that example, $n=12$, $k=7$, and the parity check matrix $h$ can be described explicitly as follows: the $7$ rows of $h$ are indexed by the vertices of the complete bipartite graph $K_{3,4}$, the $12$ columns are indexed by the $12$ edges of $K_{3,4}$, and the entry $(i,j)$ of $h$ is $1$ if and only if the edge $j$ is incident on vertex $i$. As shown in~\cite{paddock2022arkhipov}, $G(h)$ is not Abelian. 
\end{remark}

@@

\begin{definition}[$r$-local linear tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
%An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester. However, we will not need to be more specific than this. \hnote{This is probably a very vague comment that only makes sense to those who already know LTCs :)}} \hnote{Given that we've already talked about parity check matrices, it seems easier to define a local linear tester for a code $\code$ as a pair $(h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.}\tnote{Yes ok. I didn't change now but I'm in favor}
%\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. 
An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$. 
\end{definition}

@@

We state our first stability result for a code-based presentation, the presentation $G(h_\had)$ defined as~\eqref{eq:def-gh-pres} where $h_\had$ is defined above. To state the result we need to specify distributions $\mu_S$ and $\mu_R$. We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$. (Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$, because it can be seen that they follow from the other relations.)

\begin{lemma}\label{lem:had-stab}
Let $\mC$ be the class of all tracial von Neumann algebras. 
The presentation $\Z_2^t= G(h_\had)$, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mu_S,\mu_R,\mC)$ stable with $\delta(\eps)=O(\eps)$. 
\end{lemma}

@@

We introduce a family of codes that will lead to interesting presentations $G(h)$, whose stability we are able to analyze.
Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$. Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
\[
	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
\]
where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$. It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$. It follows that the linear span of all $(f(x))_{x\in \F_q^m}$, when ranging over all possible $\{c_\alpha\}$, defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.

@@

We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$. The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}. %From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$. 
The description makes use of interpolation coefficients, which are defined as follows. %For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let 
%\begin{equation}\label{eq:interp-coeff}
% \alpha_{u,v,i} = \frac{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(v-(u+i')\big)}{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(u+i-(u+i')\big)}\;.
%\end{equation}
Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
 \begin{equation}\label{eq:interp-coeff}
 \alpha_{u,v,i} = \prod_{\substack{i'=0\\i'\neq i}}^{d}  \frac{v - (u + t_{i'})}{t_i - t_{i'}}~.
 \end{equation}
These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
%\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
that for all $v \in \F_q$, 
\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+t_i)\;.\]

@@

A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$, where $S = q^m \times m \times q$, is as follows. Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times \F_q$. The $(u,j,t)$-th row of $h_{\RM}$ is the vector in $\F_q^m$ that for $i \in \{0,\ldots,d\}$ has the value $\alpha_{u,v,i}$ for $v = u + t e_j$ in the coordinate indexed by $u + t_i e_j$, the value $-1$ in the coordinate indexed by $u + te_j$, and the value $0$ everywhere else.

@@

Let $\kappa: \F_q \to \F_2^t$ denote an invertible linear map such that $\kappa(a)$ is the $\F_2$-representation of $a \in \F_q$ over some (implicitly specified) self-dual basis of $\F_q$ over $\F_2$. We extend $\kappa$ and its inverse $\kappa^{-1}$ to vectors over $\F_q$ coordinate-wise. We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$. Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$  where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$. For more details on the map $\kappa$ and its properties, see~\cite[Section 3.3]{ji2020mip}.

@@

Given an $r$-local tester $M=(h,\nu)$ for $\code$, there is a natural $\max(r,3)$-local tester $M'$ for $\code'$ which can be described as follows. Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.  We describe an $r$-local tester $M' = (h',\nu')$ for $\code'$. Informally, $h'$ contains two type of checks. First, the $A$-checks consist in the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$. Second, the $B$-checks implement the checks of $\code$ specified by $M$, directly on the Hadamard encoding. More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where 
\begin{itemize}
	\item $A \in \F^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
	\item $B \in \F^{\ell q \times nq}$ is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$. The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
\end{itemize}
Define the distribution $\nu'$ as the uniform mixture of the uniform distribution on the rows of the $A$ block matrix and the uniform distribution on the rows of the $B$ block matrix.
